---
title: "Regression model for Facebook Campaigns analysis"
author: "Fábio Rocha Campos"
date: "17 de setembro de 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Objective

Script that I use to check and predict the cost and results of Facebook Campaigns. The campaigns are based upon "click in external links", so the results that I expect are how much do I need to invest in order to get some numbers of clicks.

```{r}
### Load data
df = read.csv("./data/cmkbr_full.csv", header = TRUE, sep = ",")
```

### Pre processing

```{r, echo=FALSE}
### prepare data
names <- df$Nome.da.campanha
ID <- df$ID
df <- df[,-c(1:2)]
```

### Exploratory analysis

1. Summary

```{r, echo=FALSE}
summary(df)
```

2. Plot of distribution

```{r, echo=FALSE}
plot(df)
```

3. Correlation Summary

```{r, echo=FALSE}
cor(df)
```

4. Plot two Comparisons

```{r, echo=FALSE}
par(mfrow=c(1,2))
plot(df$Alcance ~ df$Resultados)
plot(df$Resultados ~ df$Valor.gasto..BRL.)
```

### Remove or not the Outliers

```{r, echo=FALSE}
df <- df[-c(17,42),] ## Outliers
```

### Regression Model

```{r, echo=FALSE}
model <- lm(df$Resultados ~ df$Valor.gasto..BRL.)
teste <- data.frame(x=names[-c(17,42)])
predict <- predict(model, teste)

plot(df$Valor.gasto..BRL., 
     df$Resultados, 
     xlab = "Valor gasto na Campanha (R$)",
     ylab = "Clicks em Links",
     type = "p",
     col = "blue",
     pch=1,
     cex=1.5,
     main = "Regression Model for Facebook")
points(df$Valor.gasto..BRL., predict, type="p", col="red", pch=4)
abline(model, lwd=1, col='red')
legend("topright", c("y", "y_estimado"), pch=c(1,4), col=c("blue", "red"))
```

### Residuals analysis

```{r, echo=FALSE}
plot(model)
summary(model)
```

